\LARGE \bf {\sc underworlds}: Cascading Situation Assessment for Robots

### 2017-02-28 paper.tex
Conclusion

Integration with effort like RSG-DSL~\cite{blumenthal2014towards}

>>>>

We believe this work can practically support existing robotic architectures with
state-of-the-art spatio-temporal representation capabilities. We also hope that
this line of research can lead to a better understanding of the representation
needs of modern robotic systems, and participate to the emergence of a possible
common representation platform for robots, building on previous formalisation
efforts like the RSG-DSL domain specific language~\cite{blumenthal2014towards}.
